### 2024-03-02 README.Rmd
updated vignette, struggling with figure

The **cols4all** is a new R package for selecting color palettes. "Color for all" refers to our mission that colors should be usable for not just people with normal color vision, but also for people with color vision deficiency. Currently, this package contains palettes from several popular and lesser known color palette series. Own palettes series can be added as well.

@@

![https://user-images.githubusercontent.com/2444081/210850914-cdb8a128-1b8a-4900-94d0-dfa6ca449585.png](https://user-images.githubusercontent.com/2444081/210850914-cdb8a128-1b8a-4900-94d0-dfa6ca449585.png)

@@

>>>>

**cols4all** is an R package for selecting color palettes. "Color for all" refers to our mission that colors should be usable for not just people with normal color vision, but also for people with color vision deficiency. Currently, this package contains palettes from several popular and lesser known color palette series. Own palettes series can be added as well.

@@

[<img src="figures/cols4all_table3.png" width="650"/>](figures/cols4all_table3.png)

@@

Edit color palette data

*   `c4a_duplicate` Duplicates a color palette
*   `c4a_modify` Modifies palette colors
